\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textbf{\small #2} \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%----------HEADING----------
\begin{center}
    {\Huge \scshape Chokkar Gurusamy} \\ \vspace{1pt}
     Bangalore  \\ \vspace{1pt}
    \small \raisebox{-0.1\height}\faPhone\ +91 (99408) 92858 ~ \href{mailto:chokar.g@gmail.com}{\raisebox{-0.2\height}\faEnvelope\  \underline{chokkar.g@gmail.com}} ~ 
    \href{https://linkedin.com/in/chokkarg}{\raisebox{-0.2\height}\faLinkedin\ \underline{linkedin.com/in/chokkarg}}  ~
    \href{https://github.com/chokkarg}{\raisebox{-0.2\height}\faGithub\ \underline{github.com/chokkarg}}
    \vspace{-8pt}
\end{center}

%-----------EXPERIENCE OVERVIEW-----------
\section{Experience Overview}
    \resumeSubHeadingListStart        
    \vspace{-30pt}
    \resumeSubheading    
      {}{}
      {}{} 
      
\resumeItemListStart
\resumeItem{Full Stack Developer with 12+ years of experience designing and deploying scalable, high-performance applications across web and mobile platforms.}
\resumeItem{Proficient in the full Spring ecosystem --- Spring Core, Spring MVC, Spring Data JPA, Spring Security, and Spring Cloud --- for building robust microservices architectures.}
\resumeItem{Strong background in REST API development with Circuit Breaker and Service Discovery patterns, SQL/NoSQL databases (PostgreSQL, Oracle, MongoDB), and database migrations using Liquibase.}
\resumeItem{Experienced in DevOps practices including Docker, Kubernetes, GitLab CI/CD, Grafana monitoring, and the ELK Stack.}
\resumeItem{Frontend expertise in ReactJS and Android development (Kotlin/Java), with a track record of delivering user-facing applications that drive measurable business outcomes.}
\resumeItemListEnd
    
  \resumeSubHeadingListEnd
\vspace{-20pt}
%-----------TECHNICAL SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages/Frameworks}{: Java, Spring Boot, Hibernate (ORM), Microservices, JavaScript, ReactJS, Kotlin, SQL, PostgreSQL, Oracle DB, MongoDB, Android SDK, JUnit, Swagger UI} \\
     \textbf{Technologies/Tools}{: Maven, Gradle, Docker, Kubernetes, Git, GitLab CI/CD, Jenkins} \\
     \textbf{Cloud/DevOps}{: AWS (Fargate, S3, EBS, DynamoDB), Firebase, GCP, Google Analytics, Grafana, ELK Stack} \\
     \textbf{Developer Tools}{: IntelliJ IDEA, STS, VS Code, Eclipse, Android Studio} \\
     \textbf{Certifications}{: Google Cloud Professional Data Engineer} \\
    }}
 \end{itemize}
\vspace{-16pt}

%-----------AWARDS & ACHIEVEMENTS-----------
\section{Experience / Awards / Achievements}
\resumeSubHeadingListStart
   \resumeProjectHeading
   {\textbf{Dish Network Technologies $\vert$ Lead Engineer}}{May 2022 -- Present}
       \resumeItemListStart
           \resumeItem{Received the \textbf{Dish Network Technical Excellence Award} in 2024 for outstanding contributions to advancing the company's technology capabilities.}
           \resumeItem{\textbf{Won the Dish Network Codefest 2023} for developing the Asset Management app.}
           \resumeItem{Secured \textbf{1st Runner Up} in the Dish Network Hackathon 2022 for the Employee Seat Booking app.}
           \resumeItem{Awarded the \textbf{Dish Spot Award} in 2023 for exceptional performance on key projects.}
       \resumeItemListEnd
       
   \vspace{-13pt}
   \resumeProjectHeading
   {\textbf{MSys Technologies $\vert$ Technical Architect / Lead}}{Feb 2012 -- May 2022}
   \resumeItemListStart                
       \resumeItem{Recognized as \textbf{Best Performer of the Year} in 2013, 2014, 2016, 2018, and 2019. Received the \textbf{Blog Championship Award} in 2017.}
   \resumeItemListEnd

\resumeSubHeadingListEnd


%-----------PROJECTS-----------
\section{Projects}
    \vspace{2pt}
    \resumeSubHeadingListStart    
    \resumeProjectHeading{\textbf{Dish Network Technologies $\vert$ Lead Engineer}}{May 2022 -- Present}
    
\vspace{-20pt}
\resumeProjectHeading
      {\textbf{My Dish App} $|$ \emph{Java, Spring Boot, Spring Cloud -- Microservices}}{}
\resumeItemListStart
   \resumeItem{Led requirement gathering with stakeholders and managed production deployments, ensuring high availability and monitoring application performance.}
   \resumeItem{Migrated all microservices to Spring Boot 2.7, rewriting critical code paths for improved performance and maintainability.}
   \resumeItem{Integrated Snyk security scanning into the CI pipeline to identify and remediate vulnerabilities proactively.}
\resumeItemListEnd


   \vspace{-13pt}
   \resumeProjectHeading
         {\textbf{Dish Paperless Agreement App} $|$ \emph{Java, Spring Boot, Spring Cloud -- Microservices}}{}
   \resumeItemListStart
       \resumeItem{Rewrote the entire codebase from ColdFusion to Spring Boot, improving service reliability and maintainability while resolving production defects.}
   \resumeItemListEnd
   
   \vspace{-13pt}
   \resumeProjectHeading
         {\textbf{Set-Top-Box Health App} $|$ \emph{Java, Spring Boot, Spring Cloud -- Microservices}}{}
   \resumeItemListStart
       \resumeItem{Built a real-time dashboard for monitoring and analyzing Set-Top-Box payload details across the subscriber base.}
       \resumeItem{Developed and deployed RESTful APIs to capture payload data from the UI and persist it in PostgreSQL.}
   \resumeItemListEnd
   
\vspace{-13pt}
\resumeProjectHeading
    {\textbf{In-Home Service Catalogue App} $|$ \emph{Kotlin, Android SDK, Google Analytics, Crashlytics}}{}
\resumeItemListStart
   \resumeItem{Achieved a \textbf{60\% increase in on-site technical sales} through a feature-rich mobile catalogue for field technicians.}
   \resumeItem{Developed an \textbf{offline-first mobile app} with CMS content download, reducing data usage by \textbf{40\%} and improving field accessibility.}
   \resumeItem{Built an in-house CMS enabling the marketing team to update content independently, cutting update turnaround time by \textbf{70\%}.}
\resumeItemListEnd

\vspace{-13pt}
\resumeProjectHeading
    {\textbf{Shift Allowance Management App} $|$ \emph{Java, Spring Boot, Next.js, PostgreSQL, Docker Compose, Grafana}}{}
\resumeItemListStart
   \resumeItem{Automated shift allowance calculations, eliminating manual errors and reducing administrative workload.}
   \resumeItem{Improved payroll transparency and accuracy, increasing employee satisfaction with allowance processing.}
\resumeItemListEnd

\vspace{-13pt}
\resumeProjectHeading
    {\textbf{Asset Management App} $|$ \emph{Java, Spring Boot, Next.js, PostgreSQL, Docker Compose, Redmine, Grafana}}{}
\resumeItemListStart
   \resumeItem{Led end-to-end development of this award-winning app (Codefest 2023). Containerized deployment with Grafana monitoring achieved a \textbf{70\% reduction in manual effort} and \textbf{company-wide adoption}.}
   \resumeItem{Gathered requirements from stakeholders, designed the architecture, and led implementation of the entire codebase.}
\resumeItemListEnd

\vspace{-13pt}
\resumeProjectHeading
{\textbf{Employee Seat Booking App} $|$ \emph{Java, Spring Boot, ReactJS, PostgreSQL, Docker Compose}}{}
\resumeItemListStart
\resumeItem{Led backend development using Spring Boot and Java, designing REST APIs for seamless frontend-backend integration.}
\resumeItemListEnd
    
   \resumeProjectHeading{\textbf{MSys Technologies $\vert$ Technical Architect / Lead}}{Feb 2012 -- May 2022}
   
\vspace{-20pt}
\resumeProjectHeading
{\textbf{Pivot3 -- Backend Service} $|$ \emph{Java, VMware SDK, Tomcat}}{}
\resumeItemListStart
\resumeItem{Developed a backend REST service for the Pivot3 UI plugin with comprehensive unit tests to ensure API reliability.}
\resumeItemListEnd
    
\vspace{-13pt}
\resumeProjectHeading
      {\textbf{Pivot3 -- UI Plugin} $|$ \emph{JavaScript, ReactJS}}{}
\resumeItemListStart
   \resumeItem{Built a ReactJS-based UI plugin for managing Pivot3 volumes, collaborating with the UI/UX team to deliver an intuitive interface.}
\resumeItemListEnd

\vspace{-13pt}
\resumeProjectHeading
      {\textbf{Pivot3 -- vRealize Plugin} $|$ \emph{vRealize SDK, Java, JavaScript}}{}
\resumeItemListStart
   \resumeItem{Developed a vRealize plugin integrating with VMware's vRealize suite, automating batch HCI volume creation and reducing manual effort significantly.}
\resumeItemListEnd

    
   \vspace{-13pt}
   \resumeProjectHeading
         {\textbf{Nasuni -- Cloud Data Storage App} $|$ \emph{Android SDK, Java, Firebase, Google Analytics}}{}
   \resumeItemListStart
       \resumeItem{Developed an Android cloud storage app providing reliable, secure data storage and management for enterprise users.}
   \resumeItemListEnd
    
\vspace{-13pt}
\resumeProjectHeading
      {\textbf{Spree Wearables -- Health Tracker App} $|$ \emph{Android SDK, Java, Firebase, Google Analytics}}{}
\resumeItemListStart
   \resumeItem{Developed a health tracking Android app with real-time data synchronization via Firebase and usage analytics through Google Analytics.}
\resumeItemListEnd

\vspace{-13pt}
\resumeProjectHeading
      {\textbf{Mobitaz} $|$ \emph{Java, Android SDK, Robotium}}{}
\resumeItemListStart
   \resumeItem{Developed libraries to record UI objects for automated test cases, enabling playback on multiple devices via USB or wirelessly.}
   \resumeItem{Implemented an Agent app to transmit recorded events to the server and manage device playback.}
\resumeItemListEnd

\vspace{-13pt}
\resumeProjectHeading
      {\textbf{NetApp} $|$ \emph{Java, Selenium, TestNG, Maven}}{}
\resumeItemListStart
   \resumeItem{Built a comprehensive automated test suite using Selenium WebDriver, TestNG, and Maven to validate NetApp product reliability.}
\resumeItemListEnd

    
\vspace{-10pt}
\resumeProjectHeading
      {\textbf{Auto Configuration Server} $|$ \emph{Java, Spring Framework, JBoss, Hibernate}}{}
\resumeItemListStart
   \resumeItem{Developed a REST API using Java and Spring Framework, collaborating with the Flex UI team for seamless frontend-backend integration.}
\resumeItemListEnd

    
\vspace{-13pt}
\resumeProjectHeading
    {\textbf{MSys Company Website} $|$ \emph{PHP, WordPress}}{}
\resumeItemListStart
   \resumeItem{Built the company website with the marketing team, integrated an analytics plugin, and increased customer engagement by \textbf{40\%}.}
\resumeItemListEnd
    
\resumeSubHeadingListEnd

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Anna University -- SIT, Tamil Nadu $|$ \emph{Bachelor of Information Technology}}{Aug 2007 -- May 2011}
      {}{}
          \resumeSubheading
      {VHN School, Tamil Nadu $|$ \emph{Bio-Maths}}{Apr 2005 -- May 2007}
      {}{}
  \resumeSubHeadingListEnd
 
\end{document}
