\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}
\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]
\pdfgentounicode=1

\newcommand{\resumeItem}[1]{
  \item\small{{#1 \vspace{-2pt}}}
}
\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textbf{\small #2} \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}
\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}
\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

\begin{center}
    {\Huge \scshape Chokkar Gurusamy} \\ \vspace{1pt}
     Bangalore  \\ \vspace{1pt}
    \small \raisebox{-0.1\height}\faPhone\ +91 (99408) 92858 ~ \href{mailto:chokar.g@gmail.com}{\raisebox{-0.2\height}\faEnvelope\  \underline{chokar.g@gmail.com}} ~ 
    \href{https://linkedin.com/in/chokkarg}{\raisebox{-0.2\height}\faLinkedin\ \underline{linkedin.com/in/chokkarg}}
\end{center}

\section{Professional Summary}
\resumeSubHeadingListStart
\resumeSubheading{}{}{}{}
\resumeItemListStart
\resumeItem{Staff Engineer with 14+ years architecting and delivering scalable distributed systems across web and mobile platforms. Led microservices migration serving millions of users at Dish Network.}
\resumeItem{Drove engineering-wide adoption of DevOps practices, security standards, and architectural patterns across 3+ teams. Deep expertise in Spring Cloud, event-driven architecture, and cloud-native practices on AWS.}
\resumeItem{Proven track record of technical mentoring, cross-team influence, and delivering measurable business outcomes.}
\resumeItemListEnd
\resumeSubHeadingListEnd

\section{Technical Leadership}
\resumeSubHeadingListStart
\resumeSubheading{}{}{}{}
\resumeItemListStart
\resumeItem{Drove adoption of Spring Boot 2.7 across 3 engineering teams, standardizing microservices architecture and deployment practices.}
\resumeItem{Led security transformation by integrating Snyk into CI/CD; mentored \textbf{8 engineers}, contributing to \textbf{3 promotions}.}
 \resumeItem{Established coding standards and architectural review processes adopted across engineering.}
\resumeItemListEnd
\resumeSubHeadingListEnd
\vspace{-10pt}

\section{Architecture \& Innovation}
\resumeSubHeadingListStart
\resumeSubheading{}{}{}{}
\resumeItemListStart
\resumeItem{Designed microservices architecture for My Dish App platform serving \textbf{10M+ subscribers}; established event-driven patterns using Kafka and RabbitMQ.}
\resumeItem{Championed offline-first mobile architecture, reducing data usage by \textbf{40\%} and improving field accessibility for technicians.}
\resumeItemListEnd
\resumeSubHeadingListEnd
\vspace{-10pt}

\section{Technical Skills}
\begin{itemize}[leftmargin=0.15in, label={}]
  \small{\item{
   \textbf{Languages/Frameworks}{: Java, Spring Boot, Microservices, JavaScript, ReactJS, Kotlin, SQL, PostgreSQL, Android SDK} \\
   \textbf{Technologies/Tools}{: Docker, Kubernetes, GitLab CI/CD, Jenkins, Liquibase, Snyk, Kafka, RabbitMQ} \\
   \textbf{Cloud/DevOps}{: AWS, Firebase, GCP, Grafana, ELK Stack, Prometheus, Distributed Tracing} \\
   \textbf{Architecture}{: Event-Driven Architecture, CQRS, System Design, API Design, Domain-Driven Design} \\
  }}
\end{itemize}
\vspace{-14pt}

\section{Certifications}
\begin{itemize}[leftmargin=0.15in, label={}]
 \item \small{Google Cloud Professional Data Engineer}
\end{itemize}
\vspace{-14pt}

\section{Projects}
\resumeSubHeadingListStart
\resumeProjectHeading{\textbf{Dish Network Technologies $|$ Staff Engineer}}{May 2022 -- Present}
\resumeItemListStart
 \resumeItem{\textbf{Technical Excellence Award} (2025, 2024) for advancing technology capabilities.}
 \resumeItem{\textbf{Spot Award} (2025, 2023) for exceptional performance on key projects.}
\resumeItemListEnd

\vspace{-10pt}
\resumeProjectHeading{\textbf{Kiro Mobile -- AI DevOps Command Center}}{}
\resumeItemListStart
 \resumeItem{Architected a mobile-first platform enabling developers to manage AI coding tasks from their phones --- zero-installation, real-time WebSocket updates, live code change monitoring.}
 \resumeItem{Built automated defect resolution workflows integrating Jira, Dynatrace, GitLab MRs, and unit tests; presented at \textbf{Dish Ignite 2026} and adopted by \textbf{50+ engineers}.}
\resumeItemListEnd

\vspace{-10pt}
\resumeProjectHeading{\textbf{My Dish App}}{}
\resumeItemListStart
 \resumeItem{Architected and led delivery of the flagship microservices platform, ensuring high availability across production for \textbf{10M+ subscribers}.}
 \resumeItem{Led migration of all microservices to Spring Boot 2.7, improving performance, maintainability, and deployment speed.}
 \resumeItem{Received \textbf{CPAW Award} for the My Dish App project release.}
\resumeItemListEnd

\vspace{-10pt}
\resumeProjectHeading{\textbf{In-Home Service Catalogue App}}{}
\resumeItemListStart
  \resumeItem{Achieved a \textbf{60\% increase in on-site technical sales} through an offline-first mobile catalogue for field technicians.}
  \resumeItem{Reduced data usage by \textbf{40\%} and cut content update turnaround by \textbf{70\%}.}
\resumeItemListEnd

\vspace{-10pt}
\resumeProjectHeading{\textbf{Asset Management App}}{}
\resumeItemListStart
  \resumeItem{Led end-to-end development of this award-winning app; containerized deployment with Grafana monitoring achieved a \textbf{70\% reduction in manual effort} and \textbf{company-wide adoption}.}
\resumeItemListEnd

\vspace{-10pt}
\resumeProjectHeading{\textbf{MSys Technologies $|$ Technical Architect / Lead}}{Feb 2012 -- May 2022}
\resumeItemListStart
  \resumeItem{\textbf{Best Performer of the Year} (2013, 2014, 2016, 2018, 2019). \textbf{Blog Championship Award} (2017).}
\resumeItemListEnd

\vspace{-10pt}
\resumeProjectHeading{\textbf{Pivot3 -- VMware Ecosystem}}{}
\resumeItemListStart
  \resumeItem{Developed backend REST services supporting \textbf{1000+ HCI volumes}; built UI and vRealize plugins, reducing manual effort by \textbf{60\%}.}
\resumeItemListEnd

\vspace{-10pt}
\resumeProjectHeading{\textbf{Android Mobile Apps}}{}
\resumeItemListStart
  \resumeItem{Built secure enterprise apps for Nasuni and Spree Wearables with real-time Firebase sync and analytics across thousands of active devices.}
\resumeItemListEnd

\vspace{-10pt}
\resumeProjectHeading{\textbf{QA \& Test Automation}}{}
\resumeItemListStart
  \resumeItem{Developed Mobitaz automation libraries and a NetApp regression suite, accelerating execution for \textbf{100+ scenarios} and reducing manual QA effort by \textbf{50\%}.}
\resumeItemListEnd

\resumeSubHeadingListEnd

\section{Education}
\resumeSubHeadingListStart
  \resumeSubheading
    {Anna University -- SIT, Tamil Nadu $|$ \emph{Bachelor of Information Technology}}{Aug 2007 -- May 2011}
    {}{}
\resumeSubHeadingListEnd

\end{document}
