%-------------------------
% Call Awesome Resume Template
\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
% glyphtounicode is pdfTeX-only; skip under XeTeX/Tectonic
\IfFileExists{glyphtounicode.tex}{%
  \ifdefined\pdfgentounicode\input{glyphtounicode}\fi
}{}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}
\setlength{\footskip}{5.0pt}

\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\ifdefined\pdfgentounicode\pdfgentounicode=1\fi

\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textbf{\small #2} \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
\begin{document}

%----------HEADING----------
\begin{center}
    {\Huge \scshape Chokkar Gurusamy} \\ \vspace{1pt}
     Bangalore, India (On-site / Hybrid) \\ \vspace{1pt}
    \small +91 99408 92858 ~$|$~
    \href{mailto:chokkar.g@gmail.com}{\underline{chokkar.g@gmail.com}} ~$|$~
    \href{https://linkedin.com/in/chokkarg}{\underline{linkedin.com/in/chokkarg}} ~$|$~
    \href{https://github.com/kvginnovate}{\underline{github.com/kvginnovate}}
    \vspace{-8pt}
\end{center}

%-----------PROFESSIONAL SUMMARY-----------
\section{Professional Summary}
{\small
Staff Engineer with \textbf{14+ years} owning end-to-end solution architecture for enterprise platforms---API services, event-driven integration, data access, security, observability, and operational readiness. At Dish Network, own architecture for the subscriber-facing microservices platform serving \textbf{10M+ subscribers} on Rancher-managed Kubernetes. Promoted \textbf{Lead $\rightarrow$ Staff} for org-wide Spring Boot 3 migration, Snyk security standards, and engineering practices adopted across \textbf{3+ teams}. Mentor \textbf{8 engineers} (\textbf{3 promotions}); lead architecture reviews, incident response, and senior/staff hiring. Hands-on in Java/Spring Boot REST APIs, OpenAPI, Kafka/event-driven patterns, cloud-native delivery, and quality gates. Regularly leverage AWS Kiro for architecture analysis, automated documentation/flow-diagram generation, and subagent-based code workflows. Introduced AI-powered Spring Boot modernization to Dish leadership---presented live demo of Kiro spec-driven development, automated code generation, and subagent orchestration to VP+ engineering leadership.
}
\vspace{-8pt}

%-----------TECHNICAL SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
  \small{\item{
   \textbf{Languages}{: Java, Kotlin, JavaScript, TypeScript, Python, SQL} \\
   \textbf{Backend \& APIs}{: Spring Boot 3, Spring Cloud, Hibernate, REST APIs, OpenAPI/Swagger, Resilience4j, Liquibase, Maven} \\
   \textbf{Architecture \& Integration}{: Microservices, Event-Driven Architecture, Kafka, RabbitMQ, API Gateway, Circuit Breaker, DDD, ADRs} \\
   \textbf{Frontend \& Mobile}{: ReactJS, Next.js, React Native, Android SDK --- guide React/API integration patterns} \\
   \textbf{Data}{: PostgreSQL, SQL, Oracle, MongoDB, DynamoDB, GemFire (distributed cache), Firebase} \\
   \textbf{Cloud \& Platform}{: Docker, Kubernetes (Rancher), AWS (S3, DynamoDB), GCP --- cloud-native delivery patterns transferable to AKS/Azure-class platforms} \\
   \textbf{DevOps, Security \& Quality}{: GitLab CI/CD, Jenkins, Snyk, Dynatrace, Prometheus, ELK, PagerDuty; quality gates in CI; JUnit, Selenium, Postman, API \& performance testing} \\
  \textbf{AI \& Automation}{: Kiro (spec-driven dev, hooks, subagents, EARS), MCP integrations (GitLab, Jira, GitHub), custom agent skills (defect-fix / test-gen / code-review), LLM workflows}
 }}
\end{itemize}
\vspace{-14pt}

%-----------PROFESSIONAL EXPERIENCE-----------
\section{Professional Experience}
  \resumeSubHeadingListStart

 \resumeProjectHeading{\textbf{Dish Network Technologies $\vert$ Staff Engineer} (promoted from Lead)}{May 2022 -- Present}
     \resumeItemListStart
         \resumeItem{Own platform architecture and engineering standards across API services, caching, CI/CD, security scanning, observability, and runbooks---ensuring consistency, scalability, and production readiness across multiple product teams.}
        \resumeItem{Promoted \textbf{Lead $\rightarrow$ Staff} for org-wide impact: authored Spring Boot 3 migration guide adopted across platform services; drove Snyk adoption across \textbf{3+ engineering teams}; pioneered AI-assisted workflows used by \textbf{50+ engineers}---Kiro spec-driven development, subagent orchestration, automated documentation and flow-diagram generation, and MCP-server agent skills for end-to-end automation. Presented live demo of AI-powered Spring Boot modernization to VP+ leadership, showcasing Kiro spec-driven development and automated code generation capabilities.}
        \resumeItem{Lead architecture across \textbf{3+ product teams} (\textbf{[X]+ engineers total}); mentor \textbf{8 engineers} (\textbf{3 promotions} to senior/staff); established architecture review board for platform services; lead on-call incident response with post-mortems and runbooks.}
         \resumeItem{\textbf{Annual Technical Excellence Award} (2025, 2024) $\cdot$ \textbf{Spot Award} (2025, 2023) $\cdot$ \textbf{CPAW Award} --- recognized for platform reliability, security posture, and delivery impact.}
     \resumeItemListEnd

\vspace{-12pt}
\resumeProjectHeading
   {\textbf{My Dish App -- Subscriber Platform} $|$ \emph{Java, Spring Boot 3, Spring Cloud, REST, OpenAPI, GemFire, Kafka, K8s}}{}
\resumeItemListStart
\resumeItem{Architected enterprise REST microservices (API-first / OpenAPI) for the flagship subscriber platform serving \textbf{10M+ subscribers}---directly supporting subscription revenue through high availability and sub-second API latency; defined integration patterns across frontend, backend, and shared platform services.}
\resumeItem{Led migration to \textbf{GemFire} distributed caching---reduced data-access latency and offloaded database read load; guided teams on data access patterns, performance, and reliability trade-offs (SQL/NoSQL and cache-aside).}
\resumeItem{Established event-driven integration patterns using \textbf{Kafka} and \textbf{RabbitMQ} for async workflows and service decoupling; improved resilience with circuit-breaker patterns and API gateway routing.}
\resumeItem{Drove \textbf{Spring Boot 3} migration across platform services---migration guide, guardrails, paired remediation of breaking changes; improved startup/GC behavior and unblocked security patching.}
\resumeItem{Integrated \textbf{Snyk} into GitLab CI/CD with exploitability-based triage; shortened critical vulnerability exposure from multi-day windows to same-day remediation for high-severity findings.}
\resumeItem{Built observability and operational readiness: Dynatrace APM, distributed tracing, service dashboards, PagerDuty alerting, and documented runbooks; own incident process for platform services.}
\resumeItem{Established CI quality gates and NFR discipline---unit/API tests (JUnit/Postman), security scanning, and observability checks as release prerequisites; guided teams on performance, scalability, and reliability trade-offs.}
\resumeItemListEnd

\vspace{-12pt}
\resumeProjectHeading
 {\textbf{Paperless Agreement \& STB Health} $|$ \emph{Spring Boot, REST, real-time monitoring}}{}
\resumeItemListStart
\resumeItem{\textbf{Paperless Agreement:} Led ColdFusion $\rightarrow$ Spring Boot microservices migration; eliminated chronic production failures and stabilized subscriber onboarding company-wide.}
\resumeItem{\textbf{STB Health Monitor:} Real-time dashboards and REST APIs for Set-Top-Box telemetry across \textbf{10M+ devices}, enabling proactive ops before subscriber impact.}
\resumeItemListEnd

\vspace{-12pt}
\resumeProjectHeading
   {\textbf{In-Home Service Catalogue \& Internal Tools} $|$ \emph{Kotlin/Android, Spring Boot, React/Next.js}}{}
\resumeItemListStart
 \resumeItem{\textbf{Field catalogue:} Offline-first Android app---\textbf{40\%} lower data usage; contributed to \textbf{60\%} increase in on-site technical sales; CMS cut content turnaround \textbf{70\%} (weeks $\rightarrow$ hours).}
 \resumeItem{\textbf{Internal tools:} Asset Management, Shift Allowance, Seat Booking (containerized, Dynatrace). Asset Management won \textbf{Codefest 2023}, \textbf{70\%} less manual effort, company-wide adoption; guided React/Next.js + Spring REST integration.}
\resumeItemListEnd

\vspace{-12pt}
\resumeProjectHeading
    {\textbf{Kiro Mobile -- AI DevOps Command Center} $|$ \emph{innovation / platform leverage}}{}
\resumeItemListStart
\resumeItem{Built a mobile command center for AI coding tasks---WebSocket live updates, GitLab MR status, and Dynatrace alerts; adopted by \textbf{50+ engineers} at Dish.}
\resumeItem{Authored MCP servers (GitLab, Jira) and agent skills (defect-fix, test-generation, code-review) for end-to-end incident remediation; presented at \textbf{Dish Ignite 2026}.}
\resumeItemListEnd

\vspace{-12pt}
  \resumeProjectHeading{\textbf{MSys Technologies (now Aziro) $\vert$ Technical Architect / Lead}}{Feb 2012 -- May 2022}
     \resumeItemListStart
         \resumeItem{Progressed \textbf{Software Engineer $\rightarrow$ Senior $\rightarrow$ Tech Lead $\rightarrow$ Technical Architect} over 10 years serving US clients (Pivot3, Nasuni, NetApp) in storage, virtualization, and cloud.}
         \resumeItem{Led teams of \textbf{3--8} engineers; owned scoping, architecture, demos, and delivery. Grew Pivot3 engagement from 3 to 6 engineers via delivery quality and scope expansion.}
         \resumeItem{\textbf{Best Performer of the Year} (5x: 2013, 2014, 2016, 2018, 2019) $\cdot$ \textbf{Blog Championship Award} (2017)}
     \resumeItemListEnd

\vspace{-12pt}
\resumeProjectHeading
{\textbf{Pivot3 -- VMware HCI Platform} $|$ \emph{Java, REST, ReactJS, vRealize}}{}
\resumeItemListStart
\resumeItem{Technical Lead for VMware integration: backend REST APIs, ReactJS vSphere UI plugin, and vRealize Orchestrator automation for bulk HCI volume provisioning (\textbf{1000+ volumes})---\textbf{60\%} reduction in manual provisioning effort.}
\resumeItem{Partnered with US product stakeholders on roadmap, architecture reviews, and release delivery; translated requirements into scalable technical designs.}
\resumeItemListEnd

\vspace{-12pt}
\resumeProjectHeading
{\textbf{Enterprise Mobile \& Test Automation} $|$ \emph{Android, Firebase, Selenium}}{}
\resumeItemListStart
\resumeItem{Led 3 engineers shipping Nasuni and Spree Wearables Android apps (Play Store) with Firebase sync and analytics for crash/engagement monitoring.}
\resumeItem{Built Mobitaz mobile test automation (record/playback) for client demos; delivered NetApp Selenium regression suite covering \textbf{100+ scenarios} and cutting manual regression effort by \textbf{50\%}.}
\resumeItemListEnd

\resumeSubHeadingListEnd

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Anna University -- SIT, Tamil Nadu $|$ \emph{Bachelor of Information Technology}}{2007 -- 2011}
      {}{}
  \resumeSubHeadingListEnd

\vspace{-12pt}
%-----------CERTIFICATIONS-----------
\section{Certifications}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Google Cloud Professional Data Engineer}{}{}{}
  \resumeSubHeadingListEnd

\end{document}
